Reduced MHD Manuscript

### 2025-01-27 Manuscript/Manuscript.tex
So many changes

\documentclass{article}
\usepackage[backend=biber,style=phys]{biblatex}
\addbibresource{references.bib}
\usepackage{amsmath,amsthm,amssymb,amsfonts, mathtools, braket, cancel, bm, xcolor}
\usepackage[margin=1in]{geometry}

@@

\newcommand{\para}{\parallel}
\newcommand{\lam}{\lambda}
\newcommand{\om}{\omega}
\newcommand{\gam}{\gamma}
\newcommand{\ep}{\epsilon}
\newcommand{\np}{\nabla_\perp}
\newcommand{\apo}{\ ^{\prime} \!}
\newcommand{\p}{\partial}
\newcommand{\ext}{\mathop{}\!\mathrm{d}}
\newcommand{\til}[1]{\widetilde{ #1 }}
\newcommand{\deriv}[2]{\frac{\p #1}{\p #2}}
\newcommand{\st}{\sin\theta}
\newcommand{\ct}{\cos\theta}
\newcommand{\sphi}{\sin\phi}
\newcommand{\cphi}{\cos\phi}
\newcommand{\fr}{\frac{1+\ep q}{1+\ep\beta_\para}}
\newcommand{\frinv}{\frac{1+\ep\beta_\para}{1+\ep q}}

@@

\title{Reduced MHD Manuscript}
\author{Finny Valorz}
\date{June 2024}
\begin{document}
\maketitle

1: MHD Eqns. 2: ND process and ordering. 3: Split para/perp. Alg from two. 4: Fast-Slow Attempt. 5: 2D Decomps and q. 6: Take 4 and change vars. 7: New wFSS. Appendix: Lemmas and Identities.

@@

We assume that the pressure $p=p(\rho)$ is a function only of density. Standard boundary conditions for this system of equations are
\begin{align*} 
    \bm{B}\cdot \bm{n} = 0 \quad \text{ and }\quad  \bm{v}\cdot \bm{n} = 0 \quad \text{ on }\quad \p Q,
\end{align*}
where $\bm{n}$ denotes the outward pointing unit normal on the surface $\p Q$.

@@

Because our domain factorizes, it is convenient to nondimensionalize our coordinates according to their characteristic length scales: 
\begin{align*}
    x=aX,\quad y=aY,\quad z=\frac{L}{2\pi}Z.
\end{align*}
This allows us to replace the explicit dependence on both $a$ and $L$ with just the aspect ratio $\ep = 2\pi a/L$. For example, if we multiply each equation by a factor of $a$, the standard gradient becomes $a\nabla = \np + \ep\bm{e}_Z\p_Z$, where $\np = \pth{\p_X, \p_Y, 0}$. In these coordinates, the divergenceless condition is    
\begin{align*}
    a\nabla\cdot\bm{B} = \np\cdot\bm{B}_\perp + \ep\p_Z B_Z = 0, \quad\text{or}\quad \np\cdot\bm{B}_\perp = -\ep\p_ZB_Z. 
\end{align*}

Many plasma experiments take place on large aspect-ratio toroidal domains, where the ratio $\ep = 2\pi a/L$ is small. In such experiments, the magnetic field is usually much stronger in the toroidal than the poloidal directions, and the variations are small. Density is also relatively constant when $\ep\to 0$. This behavior motivates us to examine the specific ordering where 
\begin{align*}
    \rho &= \rho_0 \pth{1+\ep r} \\
    \bm{v} &= v_0 \bm{\nu} \\ 
    \bm{B} &= B_0 \pmat{\ep\beta_x \\ \ep\beta_y \\ 1+\ep\beta_\para},
\end{align*}
with $r, \bm{\nu}, \beta_x, \beta_y,$ and $\beta_\para$ all $O\pth{1}$ in $\ep$. The constant coefficients $\rho_0, v_0,$ and $B_0$ represent values typical of a given experiment, which can be relatiely small or large. Time and pressure will be treated similarly, so that $t=t_0\tau$ and $p=p_0\pi(r)$ with $\tau,\pi(r) = O(1)$.

This scaling is similar to one taken by Strauss in 1975. In his scaling however, toroidal magnetic field fluctuations are assumed to be $O\pth{\ep^2}$, restricting the kinds of scenarios where this process can be applied. Despite density fluctuations being small for small $\ep$, he also allows variations at $O(1)$, so that 
\begin{align*}
    \rho &= \rho_0 r \\
    \bm{v} &= v_0 \bm{\nu} \\ 
    \bm{B} &= B_0 \pmat{\ep\beta_x \\ \ep\beta_y \\ 1+\ep^2\beta_\para}.
\end{align*}
These assumptions are updated in the current analysis.

When we rewrite our nondimensionalized MHD system in the following sections, we will find the following dimensionless ratios:  
\begin{align*}
    \frac{t_0 v_0}{a} = 1, \qquad 
    \frac{p_0}{\mu_0^{-1}B_0^2} = \beta_0, \qquad 
    \frac{\rho_0\,v_0^2}{p_0} = M_0^2. 
\end{align*}
The first of these establishes a particular observation timescale, where we are zoomed in on dynamics in the poloidal plane. The second and third define the plasma-beta parameter, $\beta_0$, and Mach number, $M_0$, respectively. Different orderings of these quantities in $\ep$ correspond to different regimes, where plasma behavior is characteristically different.

\section{Rescaled Evolution Equations}
\subsection{Continuity Equation}
In our new dimensionless coordinates, the continuity equation reads
\begin{align*}
    a\deriv{\rho}{t} &= -\np\cdot\pth{\rho\bm{v}_\perp} - \ep\p_Z\pth{\rho v_Z}. 
\end{align*}
\begin{align*}
    \ep\frac{a\rho_0}{t_0}\deriv{r}{\tau} &= -a\nabla\cdot\pth{\rho\bm{v}} \\ 
    &= -\rho_0v_0\np\cdot\pth{\pth{1+\ep r}\bm{\nu}_\perp} - \ep\rho_0v_0 \p_Z\pth{\pth{1+\ep r}\nu_\para} \\ 
    &= -\rho_0v_0 a\nabla\cdot\pth{\pth{1+\ep r} \bm{\nu}}, 
\end{align*}
or, identifying our scaling coefficients, 
\begin{align*} 
    \ep\deriv{r}{\tau} &= -\frac{t_0v_0}{a} a\nabla\cdot\pth{\pth{1+\ep r}\bm{\nu}}
    = -\np\cdot\pth{\pth{1+\ep r}\bm{\nu}_\perp} - \ep\p_Z\pth{\pth{1+\ep r}\nu_\para}. 
\end{align*}

\subsection{Momentum Conservation}
Equation \eqref{momentum} contains three terms which must be separated into their poloidal and toroidal components in order to identify dimensionless parameters.
\begin{align*}
    \frac{a\rho_0v_0}{t_0} \pth{1+\ep r} \deriv{\bm{\nu}}{\tau} &= \mu_0^{-1} \pth{a\nabla\times \bm{B}} \times \bm{B} - a\nabla p(\rho) - \rho \bm{v}\cdot a\nabla \bm{v}. 
\end{align*}
To isolate the evolution of $\bm{\nu}$, we will remove $\frac{\rho_0v_0}{t_0} \pth{1+\ep r}$ from both sides.

For the first term, we make use of the identity $\pth{\nabla\times\bm{B}}\times\bm{B} = \bm{B}\cdot\nabla\bm{B} - \pth{\nabla\bm{B}}\cdot\bm{B}$ to get 
\begin{align*}
    \br{\pth{a\nabla\times\bm{B}}\times\bm{B}}_Z &= \bm{B}\cdot a\nabla B_Z - \ep\pth{\p_Z\bm{B}}\cdot\bm{B} \\ 
    &= \pth{\bm{B}_\perp\cdot\np B_Z + \ep B_Z\p_Z B_Z} - \pth{\ep\bm{B}_\perp\cdot\p_Z\bm{B}_\perp + \ep B_Z\p_ZB_Z} \\ 
    &= \bm{B}_\perp\cdot \np B_Z + \ep\bm{B}_\perp\cdot \p_Z\bm{B}_\perp \\ 
    &= B_0^2 \pth{\ep^2\bm{\beta}_\perp\cdot\np\beta_\para + \ep^3 \bm{\beta}_\perp\cdot\p_Z\bm{\beta}_\perp}  \quad\text{and}
\end{align*}
Note! $\beta_\perp\cdot\p_Z\beta_\perp = \frac{1}{2}\p_Z|\beta_\perp|^2$. Which expression is handier? 
\begin{align*}
    \br{\pth{a\nabla\times\bm{B}}\times\bm{B}}_\perp &= \bm{B}\cdot a\nabla\bm{B}_\perp - \pth{\np\bm{B}}\cdot\bm{B} \\ 
    &= \pth{\bm{B}_\perp\cdot\np\bm{B}_\perp + \ep B_Z\p_Z\bm{B}_\perp} - \pth{\pth{\np\bm{B}_\perp} \cdot\bm{B}_\perp + B_Z\np B_Z} \\ 
    &= \pth{\np\times\bm{B}_\perp}\times\bm{B}_\perp + B_Z\pth{\ep\p_Z\bm{B}_\perp - \np B_Z} \\ 
    &= \ep^2 B_0^2 \pth{\np\times\bm{\beta}_\perp}\times\bm{\beta}_\perp + B_0^2 \pth{1+\ep\beta_\para} \pth{\ep^2\p_Z\bm{\beta}_\perp - \ep\np\beta_\para}. 
\end{align*}

The pressure term gives 
\begin{align*}
    \nabla p\pth{\rho} &= \frac{p_0}{a}\np\pi\pth{1+\ep r} + \bm{e}_Z \frac{2\pi p_0}{L}\p_Z\pi.
\end{align*}

\begin{align*}
    \frac{a}{t_0v_0}\frac{\rho_0v_0^2}{\mu_0^{-1}B_0^2} \pth{1+\ep r} \deriv{\bm{\nu}}{\tau} = M_0^2\beta_0 \pth{1+\ep r} \deriv{\bm{\nu}}{\tau} &= \frac{1}{B_0^2} \pth{a\nabla\times\bm{B}}\times\bm{B} - \beta_0 a\nabla\pi - M_0^2\beta_0 \bm{\nu}\cdot a\nabla\bm{\nu}. 
\end{align*}
where we've multiplied through by $a/\mu_0^{-1}B_0^2$ to make use of orderings. $a\nabla = \np + \ep\bm{e}_Z\p_Z$ makes things easier too.

\subsection{Faraday Induction}
\begin{align*} 
\deriv{B_z}{t} &= 
    \pth{B_\perp\cdot\np + B_z\p_z}v_z - \br{(v_\perp\cdot\np + v_z\p_z) + (\np\cdot v_\perp + \p_zv_z)} B_z \\
    &= B_\perp\cdot\np v_z - v_\perp\cdot\np B_z - v_z\p_zB_z - \np \cdot v_\perp B_z 
\end{align*}

>>>>

\documentclass{article}
\usepackage[backend=biber,style=phys]{biblatex}
\addbibresource{references.bib}
\usepackage{amsmath,amsthm,amssymb,amsfonts, mathtools, braket, cancel, bm, xcolor, verbatim}
\usepackage[margin=1in]{geometry}

@@

\newcommand{\para}{\parallel}
\newcommand{\lam}{\lambda}
\newcommand{\om}{\omega}
\newcommand{\gam}{\gamma}
\newcommand{\ep}{\epsilon}
\newcommand{\np}{\nabla_\perp}
\newcommand{\lap}{\Delta_\perp}
\newcommand{\p}{\partial}
\newcommand{\ext}{\mathop{}\!\mathrm{d}}
\newcommand{\til}[1]{\widetilde{ #1 }}
\newcommand{\deriv}[2]{\frac{\p #1}{\p #2}}
\newcommand{\st}{\sin\theta}
\newcommand{\ct}{\cos\theta}
\newcommand{\sphi}{\sin\phi}
\newcommand{\cphi}{\cos\phi}
\newcommand{\fr}{\frac{1+\ep q}{1+\ep\beta_\para}}
\newcommand{\frinv}{\frac{1+\ep\beta_\para}{1+\ep q}}
\newcommand{\GN}{G_\perp^N}
\newcommand{\GD}{G_\perp^D}

@@

\title{Reduced MHD Manuscript}
\author{Finny Valorz}
%\date{June 2024}
\begin{document}
\maketitle

1: MHD Eqns. 2: ND process and ordering. 3: Split para/perp. Alg from two. 4: Fast-Slow Attempt. 5: 2D Decomps and q. 6: Take EoMs and change vars. 7: New wFSS. Appendix: Lemmas and Identities.

@@

We assume that the pressure $p=p(\rho)$ is a function only of density. Standard boundary conditions for this system of equations are
\begin{align} 
    \bm{B}\cdot \bm{n} = 0 \quad \text{ and }\quad  \bm{v}\cdot \bm{n} = 0 \quad \text{ on }\quad \p Q,
\end{align}
where $\bm{n}$ denotes the outward pointing unit normal on the surface $\p Q$.

@@

Because our domain factorizes, it is convenient to nondimensionalize our coordinates according to their characteristic length scales: 
\begin{align*}
    x=aX,\quad y=aY,\quad z=\frac{L}{2\pi}Z.
\end{align*}
This split allows us to replace the explicit dependence on both $a$ and $L$ with the aspect ratio $\ep = 2\pi a/L$. For example, if we multiply each equation by a factor of $a$, the standard gradient becomes $a\nabla = \np + \ep\bm{e}_Z\p_Z$, where $\np = \pth{\p_X, \p_Y, 0}$. In these coordinates, the divergenceless condition is    
\begin{align}
    a\nabla\cdot\bm{B} = \np\cdot\bm{B}_\perp + \ep\p_Z B_Z = 0, \quad\text{or}\quad \np\cdot\bm{B}_\perp = -\ep\p_ZB_Z \quad\text{for}\quad \bm{B}_\perp = \pmat{B_X \\ B_Y \\ 0}.
\end{align}
Similarly, we use $\bm{v}_\perp = \pmat{v_X \\ v_Y \\ 0}$ to refer to the component of $\bm{v}$ perpendicular to $Z$.

Many plasma experiments take place on large aspect-ratio toroidal domains, where the ratio $\ep = 2\pi a/L$ is small. In such experiments, the magnetic field is usually much stronger in the toroidal than the poloidal directions, and the variations are small. Density is also relatively constant when $\ep\to 0$. This behavior motivates us to examine the specific ordering where 
\begin{align}
    \rho &= \rho_0 \pth{1+\ep r}, \nonumber\\
    \bm{v} &= v_0\bm{\nu} = v_0 \pmat{\bm{\nu}_\perp \\ \nu_\para}, \\ 
    \bm{B} &= B_0 \pmat{\ep\bm{\beta}_\perp \\ 1 + \ep \beta_\para}, \nonumber
\end{align}
The seven nondimensional components of $r, \bm{\nu}_\perp = \pth{\nu_X, \nu_Y, 0}^T, \nu_\para, \bm{\beta}_\perp = \pth{\beta_X, \beta_Y, 0}^T,$ and $\beta_\para$ are written at $O\pth{1}$ in $\ep$ and describe leading order variations in our seven physical variables. The constant coefficients $\rho_0, v_0,$ and $B_0$ represent values typical of a given experiment, which can be relatiely small or large. Time and pressure will be treated similarly, so that $t=t_0\tau$ and $p=p_0\pi(r)$ with $\tau,\pi(r) = O(1)$.

This scaling is similar to one taken by Strauss in 1975. In his scaling however, toroidal magnetic field fluctuations are assumed to be $O\pth{\ep^2}$, restricting the kinds of scenarios where this process can be applied. Despite density fluctuations being small for small $\ep$, he also allows variations at $O(1)$, so that 
\begin{align*}
    \rho &= \rho_0 r, \\
    \bm{v} &= v_0 \pmat{\bm{\nu}_\perp \\ \nu_\para}, \\ 
    \bm{B} &= B_0 \pmat{\ep\bm{\beta}_\perp \\ 1+\ep^2\beta_\para}.
\end{align*}
These assumptions are updated in the current analysis.

When we rewrite our nondimensionalized MHD system in the following sections, we will find the following dimensionless ratios:  
\begin{align*}
    \frac{t_0 v_0}{a} = \ep, \qquad 
    \frac{p_0}{\mu_0^{-1}B_0^2} = \beta_0, \qquad 
    \frac{\rho_0\,v_0^2}{p_0} = M_0^2. 
\end{align*}
The first of these establishes a particular observation timescale, where we are zoomed in on dynamics in the poloidal plane. The second and third define the plasma-beta parameter, $\beta_0$, and Mach number, $M_0$, respectively. Different orderings of these quantities in $\ep$ correspond to different dynamical regimes, where plasma behavior is characteristically different.

\section{Rescaled Evolution Equations}
\subsection{Continuity Equation}
In our new dimensionless coordinates, the continuity equation reads
\begin{align*}
    \ep\frac{a\rho_0}{t_0}\deriv{r}{\tau} &= -a\nabla\cdot\pth{\rho\bm{v}} = -\rho_0v_0\np\cdot\pth{\pth{1+\ep r}\bm{\nu}_\perp} - \ep\rho_0v_0 \p_Z\pth{\pth{1+\ep r}\nu_\para}, 
\end{align*}
or, identifying our scaling coefficients, 
\begin{align} 
    \deriv{r}{\tau} &= -\np\cdot\pth{\pth{1+\ep r}\bm{\nu}_\perp} - \ep\p_Z\pth{\pth{1+\ep r}\nu_\para}. 
\end{align}

\subsection{Momentum Conservation}
Equation \eqref{momentum} contains three terms which must be separated into their poloidal and toroidal components in order to identify dimensionless parameters.
\begin{align*}
    \frac{a\rho_0v_0}{t_0} \pth{1+\ep r} \deriv{\bm{\nu}}{\tau} &= \mu_0^{-1} \pth{a\nabla\times \bm{B}} \times \bm{B} - a\nabla p(\rho) - \rho \bm{v}\cdot a\nabla \bm{v}. 
\end{align*}
For the first term, we make use of the identity $\pth{\nabla\times\bm{B}}\times\bm{B} = \bm{B}\cdot\nabla\bm{B} - \pth{\nabla\bm{B}}\cdot\bm{B}$ to get 
\begin{align*}
    \br{\pth{a\nabla\times\bm{B}}\times\bm{B}}_\perp &= \bm{B}\cdot a\nabla\bm{B}_\perp - \pth{\np\bm{B}}\cdot\bm{B} \\ 
    &= \pth{\bm{B}_\perp\cdot\np\bm{B}_\perp + \ep B_Z\p_Z\bm{B}_\perp} - \pth{\pth{\np\bm{B}_\perp} \cdot\bm{B}_\perp + B_Z\np B_Z} \\ 
    &= \pth{\np\times\bm{B}_\perp}\times\bm{B}_\perp + B_Z\pth{\ep\p_Z\bm{B}_\perp - \np B_Z} \\ 
    &= \ep^2 B_0^2 \pth{\np\times\bm{\beta}_\perp}\times\bm{\beta}_\perp + \ep B_0^2 \pth{1+\ep\beta_\para} \pth{\ep\p_Z\bm{\beta}_\perp - \np\beta_\para} \quad\text{and}
\end{align*}
\begin{align*}
    \br{\pth{a\nabla\times\bm{B}}\times\bm{B}}_\para &= \bm{B}\cdot a\nabla B_Z - \ep\pth{\p_Z\bm{B}}\cdot\bm{B} \\ 
    &= \pth{\bm{B}_\perp\cdot\np B_Z + \ep B_Z\p_Z B_Z} - \pth{\ep\bm{B}_\perp\cdot\p_Z\bm{B}_\perp + \ep B_Z\p_ZB_Z} \\ 
    &= \bm{B}_\perp\cdot \np B_Z - \ep\bm{B}_\perp\cdot \p_Z\bm{B}_\perp \\ 
    &= \ep^2B_0^2 \pth{\bm{\beta}_\perp\cdot\np\beta_\para - \ep\bm{\beta}_\perp\cdot\p_Z\bm{\beta}_\perp}.
\end{align*}
%Note! $\beta_\perp\cdot\p_Z\beta_\perp = \frac{1}{2}\p_Z|\beta_\perp|^2$. Which expression is handier? 
The second and third terms are just   
\begin{align*}
    a\nabla p &= p_0\pth{\np\pi + \ep\bm{e}_Z\p_Z\pi}, \quad\text{and} \\ 
    \rho\bm{v}\cdot a\nabla\bm{v} &= \rho_0v_0^2 \pth{1+\ep r} \pth{\bm{\nu}_\perp\cdot\np\bm{\nu} + \ep\nu_\para\p_Z\bm{\nu}}, 
\end{align*}
where derivatives of pressure are taken by expanding about $r=0$:
\begin{align*}
    \pi\pth{1+\ep r} &= \pi(1) + \pi'(1)\ep r + \frac{1}{2}\pi''(1)\pth{\ep r}^2 + \cdots = \sum_{n=1}^\infty \frac{\pi^{n}(1)}{n!}\pth{\ep r}^2.
\end{align*}

Altogether, after canceling dimensional constants and identifying scaling parameters, we get evolution equations for $\bm{\nu}_\perp$ and $\nu_\para$:  
\begin{align}
    \pth{1+\ep r} \deriv{\bm{\nu}_\perp}{\tau} &= \ep^3 \frac{1}{M_0^2\beta_0} \pth{\np\times\bm{\beta}_\perp}\times\bm{\beta}_\perp + \ep^2\frac{1}{M_0^2\beta_0} \pth{1+\ep\beta_\para} \pth{\ep\p_Z\bm{\beta}_\perp - \np\beta_\para} \nonumber\\ 
    &- \ep\frac{1}{M_0^2\beta_0}\beta_0\np\pi - \ep\pth{1+\ep r} \pth{\bm{\nu}_\perp\cdot\np\bm{\nu}_\perp + \ep\nu_\para\p_Z\bm{\nu}_\perp}, \\ 
    \pth{1+\ep r} \deriv{\nu_\para}{\tau} &= \ep^3\frac{1}{M_0^2\beta_0} \pth{\bm{\beta}_\perp\cdot\np\beta_\para - \ep\bm{\beta}_\perp\cdot\p_Z\bm{\beta}_\perp} \nonumber\\ 
    &- \ep^2\frac{1}{M_0^2\beta_0}\beta_0 \p_Z\pi - \ep\pth{1+\ep r} \pth{\bm{\nu}_\perp\cdot\np\nu_\para + \ep \nu_\para\p_Z\nu_\para}.
\end{align}

\subsection{Faraday Induction}
Similarly, we will split Faraday's Law into components parallel and perpendicular to $Z$ using
\begin{align*}
    \deriv{\bm{B}}{t} &= \nabla\times\pth{\bm{v}\times\bm{B}} = \pth{\bm{B}\cdot\nabla} \bm{v} + \cancel{\pth{\nabla\cdot\bm{B}}} \bm{v} - \pth{\bm{v}\cdot\nabla} \bm{B} - \pth{\nabla\cdot\bm{v}} \bm{B}.
\end{align*}
This gives
\begin{align}\label{faradayperp}
a\deriv{\bm{B}_\perp}{t} = \ep\frac{aB_0}{t_0} \deriv{\bm{\beta}_\perp}{\tau} 
    &= \pth{\bm{B}_\perp\cdot\np + \ep B_Z\p_Z}\bm{v}_\perp - \pth{\bm{v}_\perp\cdot\np + \ep v_Z\p_Z}\bm{B}_\perp - \pth{\np\cdot\bm{v}_\perp + \ep \p_Zv_Z}\bm{B}_\perp \nonumber\\ 
    &= \np\times\pth{\bm{v}_\perp\times\bm{B}_\perp} + \ep\pth{\p_ZB_Z + B_Z\p_Z}\bm{v}_\perp - \ep\pth{\p_Zv_Z + v_Z\p_Z}\bm{B}_\perp \nonumber\\ 
    &= \ep\p_Z\pth{B_Z\bm{v}_\perp - v_Z\bm{B}_\perp} - \bm{e}_Z\times\np\pth{\bm{e}_Z\cdot\bm{v}_\perp\times\bm{B}_\perp} \\
    \Longrightarrow \deriv{\bm{\beta}_\perp}{\tau} &= \ep\p_Z\pth{\pth{1+\ep\beta_\para}\bm{\nu}_\perp - \ep\nu_\para\bm{\beta}_\perp} - \ep\bm{e}_Z\times\np\pth{\bm{e}_Z\cdot\bm{\nu}_\perp\times\bm{\beta}_\perp}
    %\np\times\pth{\bm{v}_\perp\times\bm{B}_\perp} &= \pth{B_\perp\cdot\np - \ep\p_ZB_Z} v_\perp - \pth{v_\perp\cdot\np + \np\cdot v_\perp} B_\perp
\end{align}
\begin{align} \label{faradaypara}
a\deriv{B_Z}{t} = \ep \frac{aB_0}{t_0} \deriv{\beta_\para}{\tau} &= 
    \pth{\bm{B}_\perp\cdot\np + \ep B_Z\p_Z}v_Z - \pth{\bm{v}_\perp\cdot\np + \ep v_Z\p_Z} B_Z - \pth{\np\cdot\bm{v}_\perp + \ep \p_Zv_Z} B_Z \nonumber \\
    &= \bm{B}_\perp\cdot\np v_Z - \bm{v}_\perp\cdot\np B_Z - \ep v_Z\p_ZB_Z - \pth{\np\cdot\bm{v}_\perp} B_Z \nonumber \\ 
    \Longrightarrow \deriv{\beta_\para}{\tau} &= \ep\bm{\beta}_\perp\cdot\np\nu_\para - \ep \bm{\nu}_\perp \cdot\np\beta_\para - \ep^2 \nu_\para\p_Z\beta_\para - \pth{\np\cdot\bm{\nu}_\perp} \pth{1+\ep\beta_\para}.
\end{align}
Line \eqref{faradayperp} was obtained by recognizing that $\bm{v}_\perp\times\bm{B}_\perp = \pth{\bm{e}_Z\cdot\bm{v}_\perp\times\bm{B}_\perp}\bm{e}_Z$ lies entirely in the $Z$ direction.

\section{Fast-Slow Systems: First Attempt}
Notice that when $\ep$ is small, some of the time derivatives above are much smaller than others, so that those variables appear almost static relative to the others. The framework of fast-slow dynamical systems helps formalize this distinction.

\begin{definition}[Fast-Slow System]
    A fast-slow dynamical system (with fast variable $y\in Y$ and slow variable $x\in X$) is one whose equations of motion depend smoothly on $\ep$,
    \begin{align*}
        \frac{dy}{d\tau} = \dot{y} &= f_\ep(x,y) = f_0 + \ep f_1 + \ep^2 f_2 + \cdots \\ 
        \frac{dx}{d\tau} = \dot{x} &= \ep g_\ep(x,y) = \ep \pth{g_0 + \ep g_1 + \ep^2 g_2 + \cdots},
    \end{align*}
    while satisfying the constraint:
    \begin{align} \label{constraint}
        D_yf_0(x,y): Y \rightarrow Y \ \text{is invertible whenever}\ f_0(x,y)=0.
    \end{align}
\end{definition}

The limit system $\dot{y}=f_0$, $\dot{x}=0$ is obtained by taking $\ep\to 0$. By (Lemma \ref{limitsystem}), only the limit system needs to obey constraint \eqref{constraint} to be fast-slow.

In Section \ref{asymptotic corrections}, we will show that the trajectories of fast variables can be written as a function of slow variables according to the expansion, $y^*_\ep(x) = y^*_0 + \ep y^*_1 + \cdots$. In some cases $y^*_\ep(x)$ is not unique, and there is instead a family of possible fast trajectories. This occurs when $D_yf_0$ is only surjective instead of invertible. These systems are called ``weakly fast-slow."

Our evolution equations have some terms that appear at different orders depending on $M_0$ and $\beta_0$. We will consider three regimes, each having $M_0^2\beta_0=\ep^2$. Then, to find our limit system, we take $\ep\to0$ and see which terms remain. Doing this in all three cases suggests a fast slow split where 
\begin{align*}
    x = (\nu_\parallel,\bm{\beta}_\perp),\quad y = (r,\bm{\nu}_\perp,\beta_\parallel).
\end{align*}

\subsection{Low-$\beta$ Scaling}
In low-$\beta$ scaling, $M_0^2 = 1$, $\beta_0 = \ep^2$, the limiting fast-variable evolution equations become
\begin{align*}
\p_\tau r &= -\np\cdot\bm{\nu}_\perp\\
\p_\tau \bm{\nu}_\perp & = -\np\beta_\para\\
\p_\tau \beta_\para & = -\np\cdot\bm{\nu}_\perp.
\end{align*}
This choice of dependent variables does not comprise a fast-slow split because $D_yf_0(x,y)$ is neither injective nor surjective, so it fails to satisfy the constraint \eqref{constraint}. The derivatives in
\begin{equation} \begin{split}
    D_yf_0(x,y) [\delta y] = \pth{\deriv{f_0^j}{y^i} \br{\delta y^i}} 
    &= \pmat{\deriv{}{r}f_0^r & \deriv{}{\bm{\nu}_\perp}f_0^r & \deriv{}{\beta_\para}f_0^r\\ \deriv{}{r}f_0^{\bm{\nu}_\perp} & \ddots & \vdots \\ \deriv{}{r}f_0^{\beta_\para} & \cdots & \deriv{}{\beta_\para}f_0^{\beta_\para}} 
    \bmat{\delta r \\ \delta \bm{\nu}_\perp \\ \delta \beta_\para} \\
    &= \pmat{0 & -\np \cdot & 0 \\ 0 & 0 & -\np \\ 0 & -\np \cdot & 0} 
    \bmat{\delta r \\ \delta \bm{\nu}_\perp \\ \delta \beta_\para}
    = \pmat{-\np \cdot \delta \bm{\nu}_\perp \\ -\np \delta \beta_\para \\ -\np \cdot \delta \bm{\nu}_\perp }.
\end{split} \end{equation}
are found using $\p f_0^j/\p y^i \br{\delta y^i} = \frac{d}{d\alpha} f_0^j \pth{y^i+ \alpha \delta y^i}$.  
\begin{proof} [Injectivity:] 
    A linear map is injective if and only if its kernel is $\{0\}$. Let $\delta y = \pth{\delta r,0,0}$ for some $\delta r\neq 0$. $\delta y \in\ker D_yf_0$, so $D_yf_0$ is not injective.
\end{proof}
\begin{proof} [***Surjectivity:] 
    Given any $\delta\bar{y}\in Y$, we are unable to construct a $\delta y\in Y$ for which $D_yf_0[\delta y] = \delta\bar{y}$.  $\delta r$
\end{proof}

Intuitively, a fast-slow system ought to change on the fast timescale with a change in one of its fast variables. The system above is degenerate in the fast variable $r$, which suggests there are hidden slow variables among these fast variables.

\subsection{High-$\beta$ Scaling}
In the high-$\beta$ scaling $M_0^2 = \ep$, $\beta_0 = \ep$, the limiting fast-variable evolution equations are identical to the low-$\beta$ scaling, and so do not comprise a fast-slow split:
\begin{align*}
\p_\tau r & = -\np\cdot\bm{\nu}_\perp\\
\p_\tau \bm{\nu}_\perp & = -\np\beta_\para\\
\p_\tau \beta_\para & = -\np\cdot\bm{\nu}_\perp.
\end{align*}

\subsection{Low-Flow Scaling}
In low-flow scaling, $M_0^2 = \epsilon^2$, $\beta_0 = 1$ (where $\beta_0$ is actually larger than in high-$\beta$), the limiting fast-variable evolution equations are
\begin{align*}
\p_\tau r &= -\np\cdot\bm{\nu}_\perp\\
\p_\tau \bm{\nu}_\perp & = -\np (\pi^\prime(1)r + \beta_\para)\\
\p_\tau \beta_\para & = -\np\cdot\bm{\nu}_\perp.
\end{align*}
This time, fast directional derivative looks like 
\begin{align} 
    D_yf_0(x,y) [\delta y] 
    &= \pmat{0 & -\np \cdot & 0 \\ -\pi'(1)\np & 0 & -\np \\ 0 & -\np \cdot & 0}
    \bmat{\delta r \\ \delta \bm{\nu}_\perp \\ \delta \beta_\para} = \pmat{-\np \cdot \delta \bm{\nu}_\perp \\ -\np \pth{\pi'(1)\delta r + \delta \beta_\para} \\ -\np \cdot \delta \bm{\nu}_\perp}.
\end{align}
Although this system is no longer degenerate in $r$, it still fails to satisfy condition (\ref{constraint}). 
\begin{proof} [Injectivity:]
    $\delta y+c\in\ker D_yf_0$ for any $\delta y=0$ and constant $c$. 
\end{proof}
\begin{proof} [Surjectivity:]
    ***
\end{proof}

In each regime, the fact that the apparent fast-slow split is not correct suggests there is a nicer set of dependent variables to describe ideal MHD that cleanly separates fast and slow dynamics. The following section is devoted to identifying such variables.

\section{Nicer Dependent Variables for MHD}
Given any planar vector field $\bm{w}_\perp$ on a domain $D$ diffeomorphic to the unit disc with $\bm{n}\cdot\bm{w}_\perp = 0$ on $\partial D$, there are unique scalar fields $\phi,\psi:D\rightarrow\mathbb{R}$ such that
\begin{align}
\bm{w}_\perp = \np\phi + \bm{e}_Z\times\np\psi,\quad \bm{n}\cdot\np\phi = 0\text{ on }\partial D,\quad \int_D\phi \,dxdy = 0,\quad \psi = 0\text{ on }\partial D.\label{potential_rep}
\end{align}
The scalars are determined from $\bm{w}_\perp$ by solving the pair of Poisson equations given by
\begin{align} \label{poisson}
    \lap\phi = \np\cdot\bm{w}_\perp, && \lap\psi = \bm{e}_Z\cdot \np\times\bm{w}_\perp,
\end{align}
subject to the boundary conditions listed in \eqref{potential_rep}. As described in the appendix (\ref{}), these equations can be inverted by the Green's operators $\GN:L^2\to\mathcal{N}$ and $\GD:L^2\to\mathcal{D}$, where $\mathcal{N}$ and $\mathcal{D}$ are spaces of $L^2$ functions with homogeneous Neumann and Dirichlet boundary conditions on the disc, respectively:
\begin{align*}
    \phi = \GN\lap\phi = \GN\pth{\np\cdot\bm{w}_\perp}, && \psi = \GD\lap\psi = \GD\pth{\bm{e}_Z\cdot\np\times\bm{w}_\perp}.
\end{align*}

For each fixed $Z$, these considerations apply to the vector fields $\bm{\nu}_\perp$ and $\bm{\beta}_\perp$. Thus, there are ($Z$-dependent) scalar fields $\phi,\psi,\Phi,\Psi$ such that
\begin{align*}
\bm{\nu}_\perp & = \np\phi + \bm{e}_Z\times \np\psi\\
\bm{\beta}_\perp & = \np\Phi + \bm{e}_Z\times \np\Psi,
\end{align*}
and
\begin{gather*}
\psi = \Psi = 0 \text{ on } \p D,\quad \bm{n}\cdot\np\phi = \bm{n}\cdot\np\Phi = 0 \text{ on } \p D,\quad \iint_D \phi\ dxdy = \iint_D \Phi\ dxdy = 0,
\end{gather*}
where $D$ denotes the poloidal cross section of the spatial domain $Q$. We name the spaces of functions with homogeneous Dirichlet and Neumann boundary conditions $\psi,\Psi\in\mathcal{D}$ and $\phi,\Phi\in\mathcal{N}$, respectively. We will exchange the dependent variables $\bm{\beta}_\perp,\bm{\nu}_\perp$ with the four scalars $\phi,\Phi,\psi,\Psi$.

Note that the divergenceless magnetic field constraint, $\nabla\cdot\bm{B} = \np\cdot\bm{\beta}_\perp + \ep\p_Z\beta_\para = \lap\Phi + \ep\p_Z\beta_\para = 0$ actually lets us ignore one degree of freedom in $\bm{\beta}_\perp$. Specifically, $\Phi = -\ep\GN\p_Z\beta_\para$ is determined uniquely by $\beta_\para$. It is still convenient to write some equations with $\bm{\beta}_\perp$ and $\Phi$ though.
